---
title: "Rangking Plot"
author: "Ujang Fahmi & Frey"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    fig_caption: yes
    toc: 3
vignette: >
  %\VignetteIndexEntry{Rangking Plot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, warning = FALSE, message = FALSE, fig.align='center', fig.width=7, fig.height=5,
  comment = "#>"
)
```

## Introduction

Used to compare the position or performance of multiple items with respect to each other. Actual values matters somewhat less than the ranking.

## Lollipop

Lollipop chart sebenarnya hampir sama dengan bar chart. Namun salah satu kelebihannya adalah plot menjadi tidak terlalu penuh, karena direprsentasikan dengan point dan garis saja. Berikut adalah contohnya. 

```{r}
library(dataplot)
library(ggplot2)

df <- data.frame(
  "brand" = c("Samsung", "Huawei", "Apple", "Xiaomi", "OPPO"),
  "share" = c(10, 30, 20, 35, 5)
)

plot_lollipop(data = df, x = "brand", y = "share",
              title = "Lorem Ipsum is simply dummy text",
              subtitle = "Contrary to popular belief, Lorem Ipsum is not simply random text",
              data_source = "www.kedata.online"
              )
```


